Modal Abstractions for Virtualizing Memory Addresses

### 2023-03-03 programlogic.tex
fixed compilation

\begin{figure*}
  \[
  \begin{array}{l}
\begin{array}{l}
  \vaddr\mapsto_{\textsf{v}}\{\textsf{q}\}\vpage \stackrel{def}{=} \lambda \crthree.\\
  \exists_{\entryf \;, \entrytr \;, \entrytw \;,\entryo} \ldotp

@@

Readers familiar with dynamic frames~\cite{parkinson2011relationship} might find it useful to notice that a different perspective on this matter is that virtual points-to assertions are self-stable \emph{except} for changes in \lstinline|cr3|, so framing would then naturally require other means of holding \lstinline|cr3| constant (or saving and restoring it).
Virtual points-to assertions could be made self-stable by also giving them partial ownership over \lstinline|cr3| assertions, but this would require explicitly plumbing that ownership from \emph{all} assertions back to any place an address space change might occur; this would seem to be a far graver loss of modularity than this extra quirk in framing discussions.
\begin{figure}
\begin{mathpar}
\inferrule[WriteToRegFromReg]{
  \{P \ast r_d \mapsto_{r} \texttt{rvs} \ast r_s \mapsto_{r}\{q\} \texttt{ rvs} \}\;\overline{ is}
}{
  \{P \ast r_d \mapsto_{r} \texttt{rvd} \ast r_s \mapsto_{r}\{q\} \texttt{ rvs} \}
  \texttt{ mov}~\texttt{r}_d,~\texttt{r}_s;\;\overline{is}
  %\lstinline|mov %cr3, r| 
}
\\
\inferrule[WriteToMemFromReg]{
  \{P \ast r_s \mapsto_{r}\{q\}  \texttt{rvs} \ast \lstinline|cr3| \mapsto_{r} \texttt{cr3val}  \ast r_a \mapsto_{r} \{q\} \texttt{ vaddr} \ast \texttt{vaddr} \mapsto_{t,\texttt{cr3val}} \texttt{v} \}\;\overline{ is}  
}{
  \{P \ast r_s \mapsto_{r}\{q\}  \texttt{rvs} \ast \lstinline|cr3| \mapsto_{r} \texttt{cr3val}  \ast r_a \mapsto_{r}\{q\} \texttt{ vaddr} \ast \texttt{vaddr} \mapsto_{t,\texttt{cr3val}} \texttt{rvs} \}
  \texttt{ mov}~\texttt{r}_a,~\texttt{r}_s;\;\overline{is}
}
\\
\inferrule[WriteToRegFromMem]{
  \{P \ast r_d \mapsto_{r}  \texttt{v} \ast \lstinline|cr3| \mapsto_{r} \texttt{cr3val}  \ast r_a \mapsto_{r} \{q\} \texttt{ vaddr} \ast \texttt{vaddr} \mapsto_{t,\texttt{cr3val}} \texttt{v} \}\;\overline{is}
}{
  \{P \ast r_d \mapsto_{r}  \texttt{rvd} \ast \lstinline|cr3| \mapsto_{r} \texttt{cr3val}  \ast r_a \mapsto_{r} \{q\} \texttt{ vaddr} \ast \texttt{vaddr} \mapsto_{t,\texttt{cr3val}} \texttt{v} \}
  \texttt{mov}~\texttt{r}_d,~\texttt{r}_a;\;\overline{is}
}
\\
\inferrule[WriteToRegCtlFromReg]{
  \{P \ast r_s \mapsto_{r}\{q\}  \texttt{ rvs} \ast \lstinline|cr3| \mapsto_{r} \texttt{rvs}  \}\overline{is}
}{
  \{P \ast r_s \mapsto_{r}\{q\}  \texttt{ rvs} \ast \lstinline|cr3| \mapsto_{r} \texttt{cr3val}  \}
  \texttt{mov}~\texttt{cr3},~r_s;\;\overline{is}
  %\lstinline|mov %cr3, r| 
}
\end{mathpar}
\caption{Selected Reasoning Rules for ..}
\label{fig:wpdamd}
\end{figure}

>>>>

\begin{figure*}
  \[
  \begin{array}{l}
\begin{array}{l}
  \vaddr\mapsto_{\textsf{t}}\{\textsf{q}\}\vpage \stackrel{def}{=} \lambda \crthree.\\
  \exists_{\entryf \;, \entrytr \;, \entrytw \;,\entryo} \ldotp

@@

Readers familiar with dynamic frames~\cite{parkinson2011relationship} might find it useful to notice that a different perspective on this matter is that virtual points-to assertions are self-stable \emph{except} for changes in \lstinline|cr3|, so framing would then naturally require other means of holding \lstinline|cr3| constant (or saving and restoring it).
Virtual points-to assertions could be made self-stable by also giving them partial ownership over \lstinline|cr3| assertions, but this would require explicitly plumbing that ownership from \emph{all} assertions back to any place an address space change might occur; this would seem to be a far graver loss of modularity than this extra quirk in framing discussions.
\begin{figure}
\begin{mathpar}
\inferrule[WriteToRegFromReg]{
  \{P \ast r_d \mapsto_{r} \textsf{rvs} \ast r_s \mapsto_{r}\{q\} \textsf{ rvs} \}\;\overline{ is}
}{
  \{P \ast r_d \mapsto_{r} \textsf{rvd} \ast r_s \mapsto_{r}\{q\} \textsf{ rvs} \}
  \textsf{ mov}~\textsf{r}_d,~\textsf{r}_s;\;\overline{is}
  %\lstinline|mov %cr3, r| 
}
\\
\inferrule[WriteToMemFromReg]{
  \{P \ast r_s \mapsto_{r}\{q\}  \textsf{rvs} \ast \textsf{cr3} \mapsto_{r} \textsf{cr3val}  \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{t},\textsf{cr3val}} \textsf{v} \}\;\overline{ is}  
}{
  \{P \ast r_s \mapsto_{r}\{q\}  \textsf{rvs} \ast \textsf{cr3} \mapsto_{r} \textsf{cr3val}  \ast r_a \mapsto_{r}\{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{t},\textsf{cr3val}} \textsf{rvs} \}
  \textsf{ mov}~\textsf{r}_a,~\textsf{r}_s;\;\overline{is}
}
\\
\inferrule[WriteToRegFromMem]{
  \{P \ast r_d \mapsto_{r}  \textsf{v} \ast \textsf{cr3} \mapsto_{r} \textsf{cr3val}  \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{t},\textsf{cr3val}} \textsf{v} \}\;\overline{is}
}{
  \{P \ast r_d \mapsto_{r}  \textsf{rvd} \ast \textsf{cr3} \mapsto_{r} \textsf{cr3val}  \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{t},\textsf{cr3val}} \textsf{v} \}
  \textsf{mov}~\textsf{r}_d,~\textsf{r}_a;\;\overline{is}
}
\\
\inferrule[WriteToRegCtlFromReg]{
  \{P \ast r_s \mapsto_{r}\{q\}  \textsf{ rvs} \ast \textsf{cr3} \mapsto_{r} \textsf{rvs}  \}\overline{is}
}{
  \{P \ast r_s \mapsto_{r}\{q\}  \textsf{ rvs} \ast \textsf{cr3} \mapsto_{r} \textsf{cr3val}  \}
  \textsf{mov}~\textsf{cr3},~r_s;\;\overline{is}
  %\lstinline|mov %cr3, r| 
}
\end{mathpar}
\caption{Selected Reasoning Rules for ..}
\label{fig:wpdamd}
\end{figure}
\paragraph{Register To Memory}
\paragraph{Memory To Register}
\paragraph{Register To Register}
\todo[inline,color=red]{STOP HERE}
